Homework 1 - [Zeren Li]
========================================================
  
  ### Task 1 - Implementation
  
  Use this section to implement the fizzbuzz function.


This should include a short write up describing your approach
to implementing the function. Note that both code formating / style
and your writeup matter for your overall grade.

I use a `for` loop to build this small function. Within the `for` loop, I use `if` and `else if` functions to specify the output in different conditions. First, I use `if` and `if else` functions to detect if the input contains 1) characters 2) infinite numbers 3) negative number. If the input list contains these three types of items, the function will stop with an error message, telling the user the type of their input items are not integers. After that, I programme the main part by specifying three conditions: 1) multiples of both 5 and 3 2) multiples of 5 3) multiples of 5.


```{r}
fizzbuzz = function(v) {
  for  (i in seq_along(v)) {
    if (typeof(v[i]) == "character" ) 
      {stop("The input contains characters.")}  ## error message for characters 
     else if (is.infinite(v[i]) == T) 
      {stop("The input contains infinite")}  ## error message for infinites
     else if (as.numeric(v[i]) < 0 ) 
       {stop("The input contains number smaller than zero")}  ## error message for negative number 
    else  if (v[i] %% 3  == 0 & i %% 5  == 0 ) ## condition I: multiplies of both 5 and 3
      {print("fizzbuzz") }
    else if(v[i] %% 3 == 0) ## condition II: multiplies of  3
      {print("fizz")}
    else if (v[i] %% 5  == 0) ## condition III: multiplies of 5
      {print("buzz")}
    else  print(v[i])
  }
}

```

### Task 2 - Validation

<!--
  Use this section to show the output of your 
fizzbuzz function for various inputs

No writeup is necessary for this section.
-->
  
```{r,error=T}
fizzbuzz(1)
fizzbuzz(3)
fizzbuzz(5)
fizzbuzz(15)
fizzbuzz(9:15)
fizzbuzz(15:9)

fizzbuzz(-1)
fizzbuzz(-3)
fizzbuzz(-5)
fizzbuzz(Inf)
fizzbuzz(-Inf)
fizzbuzz("A")
fizzbuzz(1.5)
fizzbuzz(1i)
fizzbuzz(4i)
```

